---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FlickrAPI

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/FlickrAPI)](https://CRAN.R-project.org/package=FlickrAPI)
[![Rdoc](http://www.rdocumentation.org/badges/version/FlickrAPI)](http://www.rdocumentation.org/packages/FlickrAPI)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/FlickrAPI)](http://www.r-pkg.org/pkg/FlickrAPI)
[![total downloads](http://cranlogs.r-pkg.org/badges/grand-total/FlickrAPI)](http://cranlogs.r-pkg.org/badges/grand-total/FlickrAPI)
<!-- badges: end -->

The goal of FlickrAPI is to provide an interface to the [Flickr API](https://www.flickr.com/services/api/) and allow R users to download data on public photos uploaded to Flickr.

## Installation

```{r, eval=FALSE}
install.packages("FlickrAPI")
# remotes::install_github("koki25ando/FlickrAPI")
```


After installing, set up a Flickr API key and save it as a local environment variable using `setFlickrAPIKey(api_key = "YOUR_API_KEY_HERE", install = TRUE)`. The Flickr API is available for non-commercial use by outside developers and is only available for commercial use under prior arrangements. Review [the Flickr API documentation](https://www.flickr.com/services/developer/), [API Overview](https://www.flickr.com/services/api/misc.overview.html), or [Flickr Developer Guide](https://www.flickr.com/services/developer/) for more information.

## Example

You can get photos from any individual user using the `getPhotos()` function.

```{r get_photos}
library(FlickrAPI)

photos <- getPhotos(user_id = "grand_canyon_nps")
knitr::kable(photos[1:4,])
```

For more information about any individual image, you can use `getPhotoInfo()` or the `getExif()` function.

```{r}
photo_info <- getPhotoInfo(photo_id = photos$id[1], output = "tags")
knitr::kable(photo_info)
```

```{r}
photo_exif <- getExif(photo_id = photos$id[10])
knitr::kable(photo_exif[1:4,])
```

You can also search photos by tag and license.

```{r}
photo_search <- getPhotoSearch(
  sort = "date-taken-desc",
  tags = c("cats", "dogs"),
  per_page = 50)

knitr::kable(photo_search[1:4,])
```


### See also

- [FlickrAPI on CRAN](https://cran.r-project.org/web/packages/FlickrAPI/index.html) ([PDF](https://cran.r-project.org/web/packages/FlickrAPI/FlickrAPI.pdf))
- [Flickr API](https://www.flickr.com/services/api/)
